ShrinkNets

### 2018-01-04 paper/paper.tex
New pass up to Evaluation

\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
\newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
\begin{document}
\title{ShrinkNets}

@@

When designing Neural Networks, finding the appropriate size (width and depth)
is key. In particular, these hyper parameters have a strong correlation with
over/underfitting \srm{give reference}. The main problem is that we have no
reliable way to find them [ref]. Decades of experimentation led to some
heuristics [ref] that try to prune that immense space of possible network sizes.
For example, researchers have used strategies such as random search,
meta-gradient descent and parser trees to reduce find good parameters without
exhaustively exploring the entire hyper-parameter space. Although these
strategies help with finding a good set of hyper-parameters, they still require
a compute-intensive search of the space.

%However, we are still bound to use costly and sometimes complex methods to find
%reasonable values for these hyper-parameters.

@@

In this paper we present a method to automatically find an appropriate network
size without paying the compute and time cost of searching through a large
hyper-parameter space. The key idea is to \emph{learn} the right network size at
the same time that the network is learning the main task. For example, for an
image classification task, with our approach we can provide the training data to
a network---without sizing it a priori---and expect to end up with a network
that has learnt the task without overfitting. This approach has two main
benefits. First, we do no longer need to choose a network size before training.
Second, the final network size will be appropriate for the task at hand, and not
larger. This is important because oversized networks have a lower inference
throughput.

@@

Filter layers have weights in the range $[0,1]$ and are placed after linear and
convolutional layers of traditional deep networks. The \textit{Filter Layer}
takes an input of size $\left(B \times C \times D_1 \times \dots \times
D_n\right)$ so it is compatible with fully connected layers with $n=0$ or
convolutional layers with $n=2$. Their crucial property is a parameter $\theta \in
\mathbb{R}^C$, defined as follows: \srm{Need to define B, C, D}.

@@

Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$
is expanded in all dimensions except the second one to match the input size. It
is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$
feature/channel will forever be $0$. When this happens, we say the Filter layer
disables the neuron. These disabled neurons/channels can be removed from the
network without changing its output (we describe how we perform this removal
below). We explain next how the weights of the Filter Layer are
adjusted during training.

@@

%\subsection{The training procedure}
\textbf{Training Procedure: } Once Filter layers are placed in a deep network, 
%To train networks we need start with a substantially oversized network, then we
%insert \textit{Filter Layers}  (usually after every linear or convolutional
%layer except the last one) and we sample their weight from the
%$\text{Uniform}(0, 1)$ distribution. 
we could train it directly and it
would be equivalent to a normal neural network. However, our goal is to find the
smallest network with reasonable performance. We achieve that by introducing
sparsity in the parameters of the \textit{Filter Layers}. Indeed, \srm{having a
negative value where?} having a negative value is equivalent to zeroing an
entire row and column in the surrounding layers. To obtain this sparsity, we
simply redefinte the loss function:

@@

The $\lambda$ parameter controls the trade-off between optimizing the original
loss or the size of the network.  \srm{Again give some intuitive description of
what is novel / important about this choice of loss function and learning
process.  It's hard to understand what is interesting/important about what you
have done without you explicitly calling it out.}

@@

To obtain good performance using this approach, it is essential to be able to
remove neurons and channels from the network as quickly as possible. This task
usually is cumbersome using existing machine learning frameworks. To enable
this, we implemented a small library on top of \textit{PyTorch} which makes it
very easy to design and train networks that contains \textit{Filter Layers}. We
will briefly describe the software architecture.  \par The key operation we want
to perform is to notify layers when a feature is removed so they can resize
themselves. Therefore, we need to track the child and parents each layer. Since
there is no concept of computation graph in \textit{PyTorch} we had to build it;
specifically,  layers are augmented with a list of incoming modules (parents)
and outgoing modules (children).  \par Edges in the graph carry features from
parent to children. When a \textit{Filter Layer} removes a feature, edges need
to notify layers of the change.  We implemented a simple event-based
architecture where edges send events about features to layers.  \srm{Suggest
cutting the following: Each  edge maintains a list of features to keep, and
called a \texttt{FeatureBag}. In many cases, layers do not change the number of
features (e.g., \textit{Dropout}, \textit{BatchNorm}), therefore, event needs to
propagate through them to notify all layers that share the same number of
features. To solve this problem, such layers instantiate
\texttt{MirrorFeatureBags} which role is to relay events to and from the root
\texttt{FeatureBag}.} With this event-based approach are able to keep all the
layers in sync. Adding layers becomes straightforward: programmers just have to
react to three events: input removal, output removal and garbage collection.
\srm{What does garbage collection do?} During our tests we ran the garbage
collection every epoch.

>>>>

\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
\newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
\newcommand{\gl}[1]{\textcolor{violet}{{\bf Gl:} #1}}
\begin{document}
\title{ShrinkNets}

@@

When designing Neural Networks, finding the appropriate size (width and depth)
is key. In particular, these hyper parameters have a strong correlation with
over/underfitting \srm{give reference} \gl{I did some litterature review and
  actually this statement is quite controversial, should we rephrase ?}. The
main problem is that we have no reliable way to find them [ref]. Decades of
experimentation led to some heuristics [ref] that try to prune that immense
space of possible network sizes.  For example, researchers have used strategies
such as random search \gl{Should we also move the references here if we remove
  the pargraph from the related work ?}, meta-gradient descent and parser trees
to reduce find good parameters without exhaustively exploring the entire
hyper-parameter space. Although these strategies help with finding a good set
of hyper-parameters, they still require a compute-intensive search of the
space.

%However, we are still bound to use costly and sometimes complex methods to
%find reasonable values for these hyper-parameters.

@@

In this paper we present a method to automatically find an appropriate network
size from a single parameter, drastically reducing the hyper-parameter
dimensionality. The key idea is to \emph{learn} the right network size at the
same time that the network is learning the main task. For example, for an image
classification task, with our approach we can provide the training data to a
network---without sizing it a priori---and expect to end up with a network that
has learnt the task without overfitting \gl{too strong, we do not really have
  any guarantee on the generalization, how about changing it to: to end up with
  a network that learnt a tradeoff between size and accuracy}. This approach
has two main benefits. First, we do no longer need to choose a network size
before training.  Second, the final network size will be appropriate for the
task at hand, and not larger \gl{Should we talk about the fact that it automatically gets rid of dead neurons ?}. This is important because oversized networks have
a lower inference throughput and higher  memory footprint.

@@

Filter layers have weights in the range $[0,+\infty]$ and are placed after
linear and convolutional layers of traditional deep networks \gl{This is how I
  used it but with the new implementation we can be more creative and put them
  anywhere, should we say "usually placed" insdead ?}. The \textit{Filter
  Layer} takes an input of size $\left(B \times C \times D_1 \times \dots
  \times D_n\right)$, where $B$ is the batch size, $C$ the number of features
(or channels), and $D$ any additional dimension. This structure makes it
compatible with fully connected layers with $n=0$ or convolutional layers with
$n=2$. Their crucial property is a parameter $\theta \in \mathbb{R}^C$, defined
as follows: \srm{Need to define B, C, D} \gl{=> done}.

@@

Where $\circ$ is the Hadamard product (pointwise multiplication) \gl{Should we
  keep only one of them to be more concise ?}, and $\theta$ is expanded in all
dimensions except the second one to match the input size. It is easy to see
that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel
will forever be $0$. When this happens, we say the Filter layer disables the
neuron. These disabled neurons/channels can be removed from the network without
changing its output (we describe how we perform this removal below). We explain
next how the weights of the Filter Layer are adjusted during training.

@@

%\subsection{The training procedure}
\textbf{Training Procedure: } Once Filter layers are placed in a deep network, 
%To train networks we need start with a substantially oversized network, then we
%insert \textit{Filter Layers}  (usually after every linear or convolutional
%layer except the last one) and we sample their weight from the
%$\text{Uniform}(0, 1)$ distribution. 
we could train it directly and it
would be equivalent to a normal neural network. However, our goal is to find the
smallest network with reasonable performance. We achieve that by introducing
sparsity in the parameters of the \textit{Filter Layers}. Indeed, having a negative component in the $\theta$ parameter of the filter layer permamently disable its associated feature \gl{Maybe redundant ? we talked about that in the previous paragraph}
. To obtain this sparsity, we simply redefine the loss function:

@@

This choice come from the Lasso loss [ref] and we use it for the same reason:
it introduces sparsity. The bigger the $\lambda$ the more entries in $\theta$
are set to zer, and since zeros entries in $\theta$ correspond to dead neurons,
lambda effectively control the number of neurons/channels in the entire
network. \srm{Again give some intuitive description of what is novel /
  important about this choice of loss function and learning process.  It's hard 
  to understand what is interesting/important about what you have done without
  you explicitly calling it out.} \gl{Is it better this way ?}

@@

\gl{Here is a shorter (clearer ?) version:}

\par \textit{Filter Vectors} can easily be implemented in a few lines of code
in many existing deep learning frameworks. However, in ShrinkNets we assume
that we start with obviously oversized networks. If disabled neurons are not
quickly removed, the overhead might caused the training process to be
significantly slower than classic neural networks. This is why we want to
support what we call garbage collection: removing the weights in the layers
that are responsible(or using) features that are disabled.
\par To be able to catpure this relationship between layers we agumented
\textit{Pytorch} (the framework we used as the foundation of our implementation)
with a graph structure very similar to the one available in Keras [ref].
In this graph edges are effectively event hubs responsible for propagating
\textit{feature removal} events to subscribing layers. ShrinkNet layers are
agumented to emit and react to these events but also propagate the event
further if has an impact at the other endpoint of the layer (input or output).
\par This event-based implementation coordinated by edges makes it very easy
to integrate new layers in the library. We even provide automatic wrapping
for layers from pytorch if they have no internal state. For more complex ones,
we provide utilitaries that makes the implementation very concise.
